`r glue::glue('Initial inferCNV results for {params$library_id}')`

### 2025-04-18 analyses/infercnv-consensus-cell-type/template-notebooks/ewings-infercnv-results.Rmd
small updates

* We used the `i6` HMM
* We used the default `analysis_mode = "subclusters"`, which allows the HMM to call CNVs at the level of clusters rather than whole samples or individual cells
* We used the following clustering parameters:
  * Leiden clustering run on PCA (not the expression matrix)
  * `k=20` nearest neighbors with a `resolution` parameter of 1 and using the `modularity` objective function

@@

```{r fig.width=12}
ggplot(query_has_cnv_df) +
  aes(x = subcluster, fill = celltype) +
  geom_bar() +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(
    vars(normal_reference),
    scales = "free_x"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

>>>>

* We used the `i6` HMM
* We used the default `analysis_mode = "subclusters"`, which allows the HMM to call CNVs at the level of clusters rather than whole samples or individual cells
* We used the default `inferCNV` clustering parameters

@@

```{r fig.width=12}
ggplot(query_has_cnv_df) +
  aes(x = subcluster, fill = forcats::fct_lump(celltype, 8)) +
  geom_bar() +
  scale_fill_brewer(palette = "Set1") +
  facet_wrap(
    vars(normal_reference),
    scales = "free_x"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
